Study of the hadronization of charged pions

### 2017-01-05 1-Answers-Review.tex

\begin{figure}[tbp]
\centering
\includegraphics[width=7.5cm] {answer-fig/VertexC.png} 
\includegraphics[width=7.5cm] {answer-fig/VertexAl.png} 
\includegraphics[width=7.5cm] {answer-fig/VertexFe.png} 
\includegraphics[width=7.5cm] {answer-fig/VertexSn.png} 
\includegraphics[width=7.5cm] {answer-fig/VertexPb.png} 
\caption {Vertex origin along $z$ (in cm) of electrons as a function of run 
number for the different solid targets.}
\label{VertexSolid}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[width=7.5cm] {answer-fig/VertexDeutC.png} 
\includegraphics[width=7.5cm] {answer-fig/VertexDeutFe.png} 
\includegraphics[width=7.5cm] {answer-fig/VertexDeutSn.png} 
\includegraphics[width=7.5cm] {answer-fig/VertexDeutPb.png} 
\caption {Vertex origin along $z$ (in cm) of electrons as a function of run 
number for the deuterium target in different solid targets configurations.}
\label{VertexLiquid}
\end{figure}

6.
P17, Fig 12 - what solid target is shown?  Are the shifts the same for electrons and pions?

{\it Sadly, this cannot be checked, the kumac used for this figure specify a file name that
do not exist anymore (codes and files have been moved at some point and non essential files
have been removed in the process). It is always possible to reproduce the figure with a root 
routine if the reviewer feel it is necessary.

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=7.5cm] {answer-fig/VertexElFe.png} 
\caption {Vertex origin along $z$ (in cm) of electrons as a function of $\phi$ 
for an iron run.}
\label{VertexEl}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[width=7.5cm] {answer-fig/VertexPipFe.png} 
\caption {Vertex origin along $z$ (in cm) of positive pions as a function of $\phi$ 
for an iron run.}
\label{VertexPip}
\end{figure}

7.
P18, Start of section 2.2.5 - I’m not sure I understand the logic in this.  If you have a drift 
chamber problem, it will be manifest in both the solid and liquid target data and the ratio of 
these should be relatively stable.  Why do you not determine run quality by looking at the 
event rate per coulomb of beam current?  For this quantity, a change in the detector 
operation will show up.

{\it You are right, the motivation for this cut is not stated properly. We are looking 
at the ratio because it would affect our result, while ignoring issues that would not
affect our observable. It is important to note that the initial run list was already
cleaned from known detector failures. (The text is corrected in the note.) }

@@

8.
P19, FIg. 14- Hard to tell how much data was discarded.  Maybe give a table of means and 
sigmas for each target or show the cuts on the figure are horizontal lines.

{\it The quantity of data removed is difficult to assess, since the problematic runs were
not passed through the final analysis. We were unable to recover the orginal values of the
fits for these specific figures and we 
lack the problematic run which have been deleted. At this stage, we do not deem necessary
to pull these old discarded data and reactivate the associated codes. If the reviewer
think it is necessary, it is time consuming but of course possible.}

@@

9.
P19 - If you use "c" constant in dimensions of Q2, then use it for W as well.

{\it Corrected.} \\

10.
P19, Sec. 2.3 - Show plots of Q$^2$, W and y with the cuts.

{\it Figures \ref{DISKine} illustrates the request and have been added to the note.} \\

\begin{figure}[tbp]
\centering
\includegraphics[width=5cm] {answer-fig/DIS-Q2.png} 
\includegraphics[width=5cm] {answer-fig/DIS-w.png} 
\includegraphics[width=5cm] {answer-fig/DIS-y.png} 
\caption {Inclusive distributions after DIS selection cuts for a sample of the iron
data.}
\label{DISKine}
\end{figure}

@@

11.
P19, eq. 7 - Is it really just the sum of weights or are they the counts multiplied by the 
weights?

{\it They are indeed the counts multiplied by the weights, which is mathematically equivalent.
The sum indicated runs over all the recorded events, it is not associated to the weights
bins or anything like that. To be implemented!!!!} \\

### 2017-01-05 chap5.tex
More questions answered...

To check the quality of the runs\footnote{Runs were formed roughly from two hours
of data, but they were much smaller in case of problems.}, we monitored the ratio of scattered electrons yields obtained from solid and liquid targets. In case of the beam hitting other materials in the beam-line or any detector is not working 
properly, this ratio will be off and indicates problematic runs. A figure 
\ref{DataQ} shows electrons yields' ratios for different nuclear target; we fitted these ratios to extract the mean value for each target, then we discarded runs that were 5~$\sigma$ away from the appropriate mean. Must note that these ratios were consistent with our target's thicknesses given in \cite{Hakobyan:2008zz} except for a carbon target. For that reason, the density of the latter was recently remeasured, and its new value was finally matching our data\footnote{i.e. (1.747+/-0.0007)g/cm$^3$ instead of 2.235 g/cm$^3$}.

@@

Since we are interested in deep inelastic scattering, we use the following 
cuts: $Q^2 > 1$~GeV$^2$/c$^2$ and $W > 2$~GeV. We also apply a cut on the energy transferred fraction, $y = \nu/E_{beam} < 0.85$. This cut aims to remove the low energy electrons that are significantly affected by radiative effects and sat at the limit of our trigger threshold.

>>>>

To check the quality of the runs\footnote{Runs were formed roughly from two hours
of data, but they were much smaller in case of problems.}, we monitored the ratio of scattered electrons yields obtained from solid and liquid targets. In case of the beam hitting other materials in the beam-line or of ony other problem that would affect our final result, 
this ratio will be off and indicate the problematic runs. A figure 
\ref{DataQ} shows electrons yields' ratios for different nuclear target; we fitted these ratios to extract the mean value for each target, then we discarded runs that were 5~$\sigma$ away from the appropriate mean. Must note that these ratios were consistent with our target's thicknesses given in \cite{Hakobyan:2008zz} except for a carbon target. For that reason, the density of the latter was recently remeasured, and its new value was finally matching our data\footnote{i.e. (1.747+/-0.0007)g/cm$^3$ instead of 2.235 g/cm$^3$}.

@@

Since we are interested in deep inelastic scattering, we use the following 
cuts: $Q^2 > 1$~GeV$^2$/c$^2$ and $W > 2$~GeV/c$^2$, with the inclusive distributions
after these cuts shown in figure \ref{DISKine}.

\begin{figure}[tbp]
\centering
\includegraphics[width=5cm] {answer-fig/DIS-Q2.png} 
\includegraphics[width=5cm] {answer-fig/DIS-w.png} 
\includegraphics[width=5cm] {answer-fig/DIS-y.png} 
\caption {Inclusive distributions after DIS selection cuts for a sample of the iron
data.}
\label{DISKine}
\end{figure}

We also apply a cut on the energy transferred fraction, $y = \nu/E_{beam} < 0.85$. This cut aims to remove the low energy electrons that are significantly affected by radiative effects and sat at the limit of our trigger threshold.
